A Study of Common Bug Fix Patterns in Rust

### 2022-11-25 related.tex
code embedding

Recent advances in deep learning has motivated researchers to build models for various types of data. A common step for building these machine learning models is to create a numerical representation of data, so that it can be fed into the model. To realize this mapping in natural languages, the researchers have proposed methods to embed word information in fixed size vectors. This process is known as word embedding. As programming languages are not that different from natural languages~\citep{hindle2016naturalness}, similar mappings have been suggested for computer programs~\citep{chen2019literature}.

\cite{alon2019code2vec} presented code2vec, a nueral model for representing code snippets as fixed size vectors. In their approach, they extracted flattened paths from the AST, and stored all the leaf-to-leaf paths. The intuition behind this decision was that leaf-to-leaf paths tend to encode more semantic information than root-to-leaf paths. They associated a fixed size vector to each path and fed them as inputs to a neural network that learns how to aggregate all these paths to a single embedding. Our code embedding approach is simpler than code2vec, as we seek a less sophisticated goal than them---bug patterns clustering instead of method name prediction. Moreover, unlike us, code2vec does not offer a general code embedding methods, since the final embedding depends on the output layer of the neural network. That is, if we change the goal of method name prediction, the embeddings would be completely different. Also, our code embedding has actual interpretability as our columns are associated with non terminals. In code2vec, the dimensions of the final vector is a parameter of the system and to no extent is related to the underlying programming language.

Our work tends to be more similar to that of \cite{hanam2016discovering}. However, our novel program embedding approach might differ from what they did on certain key decisions. In~\cite{hanam2016discovering}, they introduced the Feature Properties table, which is a categorization for program elements. Embedding programs based on this table resulted in an order-sensitive embedding, however, it made the datapoints sparse.

>>>>

Recent advances in deep learning have motivated researchers to build models for various types of data. Machine learning models require a numerical representation of the data to feed into the model. To realize this mapping for natural language text, researchers have proposed \emph{word embedding} to embed word information in fixed size vectors. As programming languages are not that different from natural languages~\citep{hindle2016naturalness}, similar mappings have been suggested for computer programs~\citep{chen2019literature}.

\cite{alon2019code2vec} presented code2vec, a neural model for representing code snippets as fixed size vectors. In their approach, they extracted flattened paths from the AST, and stored all the leaf-to-leaf paths. The intuition behind this decision was that leaf-to-leaf paths tend to encode more semantic information than root-to-leaf paths. They associated a fixed size vector with each path, and fed these as inputs to a neural network that learns how to aggregate all these paths to a single embedding. Our code embedding approach is simpler than code2vec's, as we have a specific (and simpler) goal---we aim to cluster bug patterns, not predict method names. Moreover, unlike us, code2vec does not offer a general code embedding method, since the final embedding depends on the output layer of the neural network. That is, if we change the goal of method name prediction, the embeddings would be completely different. Also, unlike many embeddings, our code embedding is interpretable: our columns are associated with non terminals. We have used the interpretability in our experiments. In code2vec, the layout of the final vector is a parameter of the system and  is not related to the underlying programming language.

Our work tends to be more similar to that of~\cite{hanam2016discovering}. However, our novel program embedding approach differs from what they did on certain key decisions. In~\cite{hanam2016discovering}, they introduced the Feature Properties table, which is a categorization for program elements. Embedding programs based on this table resulted in an order-sensitive embedding, however, it made the datapoints sparse. Our datapoints are more dense than theirs. \todo[inline]{quantify?}
